\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Assignment 5}
\author{  
  Batuhan Şekerci, 21990982\\
  Department of Computer Engineering\\
  Hacettepe University\\
  Ankara, Turkey \\
  \texttt{b21990982@cs.hacettepe.edu.tr}
}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}

\graphicspath{.}

\begin{document}
\maketitle

\section{Introduction}
In Part 1, we will create a texture to use it on a cube. Built-in features of WebGL will be used for texturing. Also there was lightning on code and we will manipulate its direction. Buttons are used to change the direction of light.
In Part 2, 
\section{Experiment}

\subsection{Part 1}
In this part, you will report your results and how you have done the first part of the experiment.

\subsection{Part 2}
In this part, you will report your results and how you have done the second part of the experiment. You will give a brief information of your classes,  methods, etc. in this subsection. Fill the tables below as expected format given as example.

\begin{table}[!ht]
  \caption{Classes}
  \label{classes}
  \centering
  \begin{tabular}{lll}
    \toprule
    \cmidrule(r){1-3}
    Class Name & Attributes & Methods\\
    \midrule
    Class\_1 & attribute1\_1, attribute1\_2, ... & method1\_1, method1\_2, ...\\
    Class\_2 & attribute2\_1, attribute2\_2, ... & method2\_1, method2\_2, ...\\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[!ht]
  \caption{Methods}
  \label{methods}
  \centering
  \begin{tabular}{llll}
    \toprule
    \cmidrule(r){1-4}
    Method Name & Input(s) & Output(s) & Info\\
    \midrule
    method\_1 & input1\_1, input1\_2, ... & output1\_1, output1\_2, ... & what method does\\
    method\_2 & input2\_1, input2\_2, ... & output2\_1, output2\_2, ... & what method does\\
    \bottomrule
  \end{tabular}
\end{table}

\section{Conclusion}
In this section, you will conclude your report. You will write what you have learned in this experiment, which parts of the experiment have been the most challenging in this assignment. \textbf{Do not forget to reference your code blocks. \cite{adams1995hitchhiker}}

\bibliographystyle{plain}
\bibliography{references}
\end{document}
